### 2009-11-13 doc/manuals/chelonia/chelonia-cli.tex
added missing arcsrmping, some more index entires

\subsubsection{stat} % (fold)
\label{ssub:stat}
With the \texttt{stat}\index{commands:chelonia:stat} method it is possible to get all the metadata about one or more entry (file, collection, etc.). The entries are specified with their Logical Name (LN).
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia stat $<$LN$>$ [$<$LN$>$ ...]}
\end{shaded}

@@

\subsubsection{makeCollection} % (fold)
\label{ssub:makecollection}
With the \texttt{makeCollection}\index{commands:chelonia:makeCollection} or \texttt{mkdir} method it is possible to create a new empty collection. The requested Logical Name (LN) should be specified.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia makeCollection $<$LN$>$}
\end{shaded}

@@

\subsubsection{unmakeCollection} % (fold)
\label{ssub:unmakecollection}
With the \texttt{unmakeCollection}\index{commands:chelonia:unmakeCollection} or \texttt{rmdir} method it is possible to delete an empty collection which is specified by its Logical Name (LN).
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unmakeCollection $<$LN$>$}
\end{shaded}

@@

\subsubsection{list} % (fold)
\label{ssub:list}
With the \texttt{list}\index{commands:chelonia:list} or \texttt{ls} method it is possible to list the contents of one or more collections which are specified by their Logical Name (LN).
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia list $<$LN$>$ [$<$LN$>$ ...]}
\end{shaded}

@@

\subsubsection{move} % (fold)
\label{ssub:move}
With the \texttt{move}\index{commands:chelonia:move} or \texttt{mv} method it is possible to move a file or collection within the namespace of chelonia (including renaming the entry). The source path and the target path should be specified as Logical Names
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia move $<$sourceLN$>$ $<$targetLN$>$}
\end{shaded}

@@

\subsubsection{putFile} % (fold)
\label{ssub:putfile}
With the \texttt{putFile}\index{commands:chelonia:putFile} or \texttt{put} method it is possible to upload a new file into the system creating a new Logical Name (LN). It is possible the specify the number of needed replicas.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia putFile $<$source filename$>$ $<$target LN$>$ [$<$number of replicas needed$>$]}
\end{shaded}

@@

\subsubsection{getFile} % (fold)
\label{ssub:getfile}
With the \texttt{getFile}\index{commands:chelonia:getFile} or \texttt{get} method it is possible to download a file specified with its Logical Name (LN). If the target local path is not given, then the file will be put into the local directory.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia getFile $<$source LN$>$ [$<$target filename$>$]}
\end{shaded}

@@

\subsubsection{delFile} % (fold)
\label{ssub:delfile}
With the \texttt{delFile}\index{commands:chelonia:delFile} or \texttt{rm} method it is possible to delete one or more files from the system.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia delFile $<$LN$>$ [$<$LN$>$ ...]}
\end{shaded}

@@

With the \texttt{modify}\index{commands:chelonia:modify} or \texttt{mod} method it is possible to modify some metadata of an entry.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia modify $<$LN$>$ $<$changeType$>$ $<$section$>$ $<$property$>$ $<$value$>$}
\end{shaded}

@@

With the \texttt{policy}\index{commands:chelonia:policy} or \texttt{pol} method it is possible to modify the policy of the entry
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia policy $<$LN$>$ $<$changeType$>$ $<$identity$>$ $<$action list$>$}   
\end{shaded}

@@

With the \texttt{unlink}\index{commands:chelonia:unlink} method it is possible to remove a file or collection just from its parent collection without removing the file or collection itself.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unlink $<$LN$>$}   
\end{shaded}

@@

\subsubsection{credentialDelegation} % (fold)
\label{ssub:credentialdelegation}
With the \texttt{credentialDelegation}\index{commands:chelonia:credentialDelegation} or \texttt{cre} method it is possible to delegate credentials to the Bartender.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia credentialDelegation}   
\end{shaded}
% subsubsection credentialdelegation (end)

\subsubsection{removeCredentials} % (fold)
\label{ssub:removecredentials}
With the \texttt{removeCredentials}\index{commands:chelonia:removeCredentials} or \texttt{rem} method it is possible to remove the previously delegated credentials.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia removeCredentials}   
\end{shaded}
% subsubsection removecredentials (end)

\subsubsection{makeMountPoint} % (fold)
\label{ssub:makemountpoint}
With the \texttt{makeMountPoint}\index{commands:chelonia:makeMountPoint} or \texttt{makemount} method it is possible to create a mount point within the namespace of Chelonia which points to a GridFTP server.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia makeMountPoint $<$LN$>$ $<$URL$>$}   
\end{shaded}

@@

\subsubsection{unmakeMountPoint} % (fold)
\label{ssub:unmakemountpoint}
With the \texttt{unmakeMountPoint}\index{commands:chelonia:unmakeMountPoint} or \texttt{unmount} method it is possible to remove a previously created mount point.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unmakeMountPoint $<$LN$>$}   
\end{shaded}

>>>>

\subsubsection{stat} % (fold)
\label{ssub:stat}
With the \texttt{stat}\index{commands:chelonia:stat}\index{chelonia:stat}  method it is possible to get all the metadata about one or more entry (file, collection, etc.). The entries are specified with their Logical Name (LN).
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia stat $<$LN$>$ [$<$LN$>$ ...]}
\end{shaded}

@@

\subsubsection{makeCollection} % (fold)
\label{ssub:makecollection}
With the \texttt{makeCollection}\index{commands:chelonia:makeCollection}\index{chelonia:makeCollection} or \texttt{mkdir} method it is possible to create a new empty collection. The requested Logical Name (LN) should be specified.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia makeCollection $<$LN$>$}
\end{shaded}

@@

\subsubsection{unmakeCollection} % (fold)
\label{ssub:unmakecollection}
With the \texttt{unmakeCollection}\index{commands:chelonia:unmakeCollection}\index{chelonia:unmakeCollection} or \texttt{rmdir} method it is possible to delete an empty collection which is specified by its Logical Name (LN).
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unmakeCollection $<$LN$>$}
\end{shaded}

@@

\subsubsection{list} % (fold)
\label{ssub:list}
With the \texttt{list}\index{commands:chelonia:list}\index{chelonia:list} or \texttt{ls} method it is possible to list the contents of one or more collections which are specified by their Logical Name (LN).
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia list $<$LN$>$ [$<$LN$>$ ...]}
\end{shaded}

@@

\subsubsection{move} % (fold)
\label{ssub:move}
With the \texttt{move}\index{commands:chelonia:move}\index{chelonia:move} or \texttt{mv} method it is possible to move a file or collection within the namespace of chelonia (including renaming the entry). The source path and the target path should be specified as Logical Names
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia move $<$sourceLN$>$ $<$targetLN$>$}
\end{shaded}

@@

\subsubsection{putFile} % (fold)
\label{ssub:putfile}
With the \texttt{putFile}\index{commands:chelonia:putFile}\index{chelonia:putFile} or \texttt{put} method it is possible to upload a new file into the system creating a new Logical Name (LN). It is possible the specify the number of needed replicas.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia putFile $<$source filename$>$ $<$target LN$>$ [$<$number of replicas needed$>$]}
\end{shaded}

@@

\subsubsection{getFile} % (fold)
\label{ssub:getfile}
With the \texttt{getFile}\index{commands:chelonia:getFile}\index{chelonia:getFile} or \texttt{get} method it is possible to download a file specified with its Logical Name (LN). If the target local path is not given, then the file will be put into the local directory.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia getFile $<$source LN$>$ [$<$target filename$>$]}
\end{shaded}

@@

\subsubsection{delFile} % (fold)
\label{ssub:delfile}
With the \texttt{delFile}\index{commands:chelonia:delFile}\index{chelonia:delFile} or \texttt{rm} method it is possible to delete one or more files from the system.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia delFile $<$LN$>$ [$<$LN$>$ ...]}
\end{shaded}

@@

With the \texttt{modify}\index{commands:chelonia:modify}\index{chelonia:modify} or \texttt{mod} method it is possible to modify some metadata of an entry.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia modify $<$LN$>$ $<$changeType$>$ $<$section$>$ $<$property$>$ $<$value$>$}
\end{shaded}

@@

With the \texttt{policy}\index{commands:chelonia:policy}\index{chelonia:policy} or \texttt{pol} method it is possible to modify the policy of the entry
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia policy $<$LN$>$ $<$changeType$>$ $<$identity$>$ $<$action list$>$}   
\end{shaded}

@@

With the \texttt{unlink}\index{commands:chelonia:unlink}\index{chelonia:unlink} method it is possible to remove a file or collection just from its parent collection without removing the file or collection itself.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unlink $<$LN$>$}   
\end{shaded}

@@

\subsubsection{credentialDelegation} % (fold)
\label{ssub:credentialdelegation}
With the \texttt{credentialDelegation}\index{commands:chelonia:credentialDelegation}\index{chelonia:credentialDelegation} or \texttt{cre} method it is possible to delegate credentials to the Bartender.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia credentialDelegation}   
\end{shaded}
% subsubsection credentialdelegation (end)

\subsubsection{removeCredentials} % (fold)
\label{ssub:removecredentials}
With the \texttt{removeCredentials}\index{commands:chelonia:removeCredentials}\index{chelonia:removeCredentials} or \texttt{rem} method it is possible to remove the previously delegated credentials.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia removeCredentials}   
\end{shaded}
% subsubsection removecredentials (end)

\subsubsection{makeMountPoint} % (fold)
\label{ssub:makemountpoint}
With the \texttt{makeMountPoint}\index{commands:chelonia:makeMountPoint}\index{chelonia:makeMountPoint} or \texttt{makemount} method it is possible to create a mount point within the namespace of Chelonia which points to a GridFTP server.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia makeMountPoint $<$LN$>$ $<$URL$>$}   
\end{shaded}

@@

\subsubsection{unmakeMountPoint} % (fold)
\label{ssub:unmakemountpoint}
With the \texttt{unmakeMountPoint}\index{commands:chelonia:unmakeMountPoint}\index{chelonia:unmakeMountPoint} or \texttt{unmount} method it is possible to remove a previously created mount point.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{chelonia unmakeMountPoint $<$LN$>$}   
\end{shaded}

### 2009-11-13 doc/manuals/user_interface/ui-data.tex
added missing arcsrmping, some more index entires

>>>>

\subsection{arcsrmping}\label{sec:arcsrmping}

The \texttt{arcsrmping}\index{arcsrmping}\index{commands:arcsrmping}
command is used to quickly test availability of an SRM service, similarly to the \textit{ping} tool in Unix.
\hspace*{0.5cm}
\begin{shaded}
   \uicommand{arcsrmping [options] $<$service$>$}
\end{shaded}
\versions{ARC 0.9}
\begin{longtable}{llp{8cm}}
    Options:&&\\
   \texttt{-t, --timeout}&\textit{seconds}&timeout in seconds (default 20)\\
   \texttt{-d, --debug}&\textit{debuglevel}&debug level, FATAL, ERROR, WARNING, INFO, VERBOSE or DEBUG - default WARNING\\
   \texttt{-z, --conffile}&\textit{filename}& configuration file (default {\$}HOME/.arc/client.conf)\\
   \texttt{-v, --version}&&print version information\\
   \texttt{-h, --help}&&print help page\\
    Arguments:&&\\
   \texttt{service} && A URL to an SRM service\\
\end{longtable}

The \texttt{arcsrmping} command is a \textit{ping} client for the SRM service. It sends an SRM ping request to the SRM service and displays the result.
